%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 
\usepackage{geometry}
\geometry{
 a4paper,
 top=25mm,
 bottom=20mm,
 }
\pagenumbering{gobble}

\begin{document}
%start comment
\iffalse
\newgeometry{top=2cm, bottom= 2cm, left=2cm,right=2cm}
%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

\namesection{GIBSON}{WONG}{ % Your name
\href{mailto:kh3wong@uwaterloo.ca}{kh3wong@uwaterloo.ca} | (647) 779-8132 % Your contact information
}
\vspace{8mm}

\begingroup
{\fontsize{14pt}{16pt}\selectfont
\begin {flushleft}
Dear Hiring Manager,\\
\end {flushleft}

\begin {flushleft}
 I’m writing to you today in regards to the job posting as a Quantitative Analyst for Citadel Investment Group LLC. I am a third year student pursuing a Bachelor of Computing and Financial Management, which is a unique degree that allows me to apply my understanding of computer programming while having a good understanding of finance to any employment opportunity. I am a passionate and hardworking individual and is excited to have a chance to work for the company. 
\end {flushleft}

\begin {flushleft}
In my most recent co-op placement, I worked as a software developer for S\&P Capital IQ. During the term, I developed features in JavaScript, accompanied with libraries like jQuery, frameworks like backbone.js and tools like Visual Studio and TortoiseSVN. Furthermore, I explored and researched new frameworks like AngularJS and identified many benefits that could occur from such a migration. Finally, I was able to improve the company's operational efficiency by automating the developers' set-up process. 
\end {flushleft}


\iffalse
\begin {flushleft}
Aside from web developement languages, I also developed skills in C++ and Python through my independent and academic studies. My interest in computer programmming is motivating me to learn new technologies including mobile developement. With a solid foundation on programming design as well as a passion for innovation, I am always ready to take on new and challenging problems. \\
\end {flushleft}
\fi

\begin {flushleft}
Aside from computer programming, I also have a strong interest in financial markets. Having completed several courses related to financial management, I have an excellent understanding of market operations, trading strategies, risk management as well as equity pricing. I also plan on taking courses such as Numeric Computation for Financial Modeling and Portfolio Optimization Models. With a solid foundation in programming and finance, I am always ready to take on new and challenging problems.
\end {flushleft}


\begin {flushleft}
Outside of class, I enjoy traveling, exploring stock market simulators, and playing sports and video games. I also enjoy taking on new projects and learning new prorgamming languages. Most importantly, I strive to make the most out of every experience and seek to learn as much as I can. \\
\end {flushleft}

\begin {flushleft}
I am equipped with the technical skills to solve any problem and, in addition to my previous work experiences, I am confident that I can be a great addition to Citadel Investment Group LLC. I would like to thank you for your valuable time and your considerations for my application. \\
\end {flushleft}

\begin {flushleft}
Sincerely,\\
\end {flushleft}

\begin {flushleft}
Gibson Wong
\end {flushleft}
}
\endgroup
%----------------------------------------------------------------------------------------


\newpage % Start a new page
\restoregeometry
%end comment
\fi
%----------------------------------------------------------------------------------------
%    RESUME
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------


\namesection{GIBSON}{WONG}{ % Your name
\href{mailto:kh3wong@uwaterloo.ca}{kh3wong@uwaterloo.ca} | (647) 779-8132 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.32\textwidth} % The left column takes up 33% of the text width of the page
%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}

%\location{Over 5000 lines:}
C \textbullet{} C++ \textbullet{} Python \textbullet{} HTML5 \\
CSS3 \textbullet{} JavaScript \textbullet{} SQL\\
%\location{Over 1000 lines:}
PowerShell \textbullet{} \LaTeX\ \textbullet{} MATLAB \\
%\location{Familiar:}
%AS3 \textbullet{} iOS \textbullet{} Android \textbullet{} MySQL

\sectionspace % Some whitespace after the section

\subsection{Frameworks \& Libraries}
backbone.js \textbullet{} AngularJS  \textbullet{} Node.js\\
jQuery \textbullet{} underscore.js \textbullet{} Jasmine\\
 
\sectionspace % Some whitespace after the section
\subsection{Tools}
Git  \textbullet{} TortoiseSVN  \\
Adobe Illustrator \textbullet{} Adobe Photoshop \\

\sectionspace % Some whitespace after the section
\subsection{In Progress}
Java \textbullet{} Mobile development
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

\section{Links} 

Github: \href{https://github.com/gibson-wong}{github.com/gibson-wong} \\
LinkedIn: \href{https://www.linkedin.com/in/kh3wong}{ca.linkedin.com/in/kh3wong} \\

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{University of Waterloo}

\descript{Bachelor of Computing and Financial Management | 3A}
\vspace{1mm}
\location{Expected Apr 2017 | Waterloo, ON }


\sectionspace % Some whitespace after the section



%------------------------------------------------
\iffalse
\subsection{Earl Haig}
\subsection{Secondary School}
\vspace{1mm}
\location{Grad. June 2012 | Toronto, Ontario}
\sectionspace % Some whitespace after the section
\fi

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

\subsection{Completed}
Data Structures and Data Management\\
{\fontsize{9.75}{11}\selectfont Object-Oriented Software Development}\\
Sequential Programming\\
Corporate Finance I\\ 

\sectionspace % Some whitespace after the section

\subsection{Ongoing}
Introduction to Scientific Computation\\
Corporate Finance II\\
Introduction to Combinatorics\\
Introduction to Optimization\\ 


\sectionspace % Some whitespace after the section
%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page


%------------------------------------------------
%Skill Summary
%------------------------------------------------

\section{Skills Summary}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
{\fontsize{11}{13}\selectfont
\begin{tightitemize}
\item Well-versed in data structures, algorithms  and OOP design concepts
\item Strong understanding of web development and MVC frameworks
\item Experienced with the Unix environment, version control, unit testing, IDEs and integrating with APIs
\item Enriched problem solving, teamwork and communication skills through leadership roles 
\end{tightitemize}
}
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{S\&P Capital IQ}
\descript{| Software Developer}

\location{Sep 2014 – Dec 2014 | Toronto, ON}
{\fontsize{11}{13}\selectfont
\begin{tightitemize}
\item Designed and implemented features for the client-side website
\item Fixed bugs and refactored JavaScript code to increase performance
\item Improved company efficiency by automating set-up processes
\item Researched AngularJS and implemented mock migrations for existing backbone.js code
\end{tightitemize}

\textbf{Key Tools:} JavaScript, jQuery, backbone.js, AngularJS, C\#, TortoiseSVN}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Bank of Montreal InvestorLine}
\descript{| E-Business Specialist	}
\location{Jan 2014 – Apr 2014 | Toronto, ON}
{\fontsize{11}{13}\selectfont
\begin{tightitemize}
\item Created wireframes and implemented the designs onto the website
\item Improved company’s productivity by revamping their analytics report
\item Provided regular maintenance and ensured up-to-date information was available on the site
\end{tightitemize}
\textbf{Key Tools:} HTML, CSS, JavaScript, Google Analytics, Adobe Photoshop }
\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{UW RED CROSS ASSOCIATION}
\descript{| Web Designer and Developer }
\location{May 2013 – Present | Waterloo, ON}
{\fontsize{11}{13}\selectfont
\begin{tightitemize}
\item Built a responsive single-page website for the club
\item Designed wireframes and mock-ups as required by the club
\item Ensured high quality results across multiple browsers and devices
\end{tightitemize}
\textbf{Key Tools:}  HTML5, CSS3, JavaScript, JQuery, Adobe Illustrator}

\sectionspace % Some whitespace after the section

%------------------------------------------------
%Projects
%------------------------------------------------

\section{Projects}
%\begin{tabular}{ll}
%UW Red Cross Association	 & Designed and constructed a responsive single-page website\\
%Compiler	 & Scanned, parsed and transformed a variation of C code into    machine language \\
%Chamber Crawler 3K	 & Applied object oriented designs in teams and implemented a rogue-like  game\\
%2013	 & National \\

%\end{tabular}

\textbf{Assembler:} Converted assembly code into machine code\\
\textbf{Compiler:} Parsed and transformed a subset of C code into assembly code \\
\textbf{CC3K:} Applied object-oriented programming to implement a rogue-like  game\\

\sectionspace % Some whitespace after the section

%------------------------------------------------
% ACTIVITES AND INTERESTS
%------------------------------------------------

\section{ACTIVITES AND INTERESTS} 
\textbf{Memberships:} UW Red Cross Association, Game Development Club\\
\textbf{Athletics:} Badminton, Ultimate Frisbee, Table Tennis \\
\textbf{Others:} Programming, Web Development, Stock Market Simulators\\


\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------


\end{document}